---
title: "example1"
author: "M Apple"
date: "2022-12-01"
output: html_document
---
# R chunk 

```{r load-data, message=FALSE}
library(tidyverse)
library(kableExtra)
library(rmarkdown)
library(ggpubr)
#comment
#load dataset
pop_data <-read_csv("data/gapminder_data.csv")

#create a table with data from euro countries in 2007 showing the countries 
#with the largest life expectancies on top

euro_data_tbl <- pop_data %>% 
  filter(continent == "Europe" & year == 2007) %>%
  select(-continent,  -year)%>%
  arrange(desc(lifeExp)) %>%
  rename(Country = country, "Population Size" = pop, "Life Expectancy" = lifeExp, 
         "GDP" = gdpPercap)
```

text text text text we ddid things now we do another r chunk

```{r create-table, message=FALSE}
euro_data_tbl %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
#kbl takes data frame as input
```

challenge to Create a new dataset euro_data_fig by filtering the pop_data tibble to contain only data from Europe. Draw a plot to display the lifeExp on the y axis and year on the x axis. Use geom_violin() to draw this as a violin plot to show the distrubution of the data across each year and save it in a euro_plot variable.

```{r create-plot, message=FALSE}
#keep on European data and change year to factor
euro_data_fig <- pop_data %>% 
                    filter(continent == "Europe")  %>% 
                    mutate(year=as_factor(year))
#Euro plot
euro_plot <- euro_data_fig %>%
                ggplot(mapping=aes(x=year, y=lifeExp)) +
                geom_violin() +
                stat_summary(fun.y = median, geom = "point")
#draw euro plot
euro_plot
```

how to displayu a massive table
```{r paged-table, message=FALSE}
paged_table(euro_data_tbl)

```

adding images
```{r add-images, message=FALSE}
uk_data_fig <- pop_data %>%
  filter(country == "United Kingdom")

#uk plot
uk_plot <- uk_data_fig%>%
  ggplot(mapping = aes(x=year, y=lifeExp))+
  geom_point()

#draw
uk_plot

#compare to euro_plot
ggarrange(uk_plot, euro_plot)

```


github token
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
